---
title: "Homework 3 Solution"
author: Yiming Zhao
output: html_document
---

```{r}
library(p8105.datasets)
library(tidyverse)
data("instacart")
```

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

The `instacart` dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns.  

Observations are the level of items in orders by user. There are user/order variables -- user ID, order day, 
and order hour, There are also item variables -- name, aisle, department, and some numeric codes.
Here is an example of observations, user 112108 made his/her fourth order at 10 am to buy 9 products: Bulgarian yogurt, organic 4% milk fat whole milk cottage cheese and so on.

How many aisles, and which are most items from?

```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```
There are 124 distinct aisles, fresh vegetables aisle is the most items ordered from.

Make a plot that shows the number of items ordered in each aisle

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x = aisle, y = n)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”.

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(aisle, desc(n)) %>% 
  knitr::kable()
``` 

Apples vs ice cream

```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  )
```


## Problem 2

Load, tidy, and otherwise wrangle the data. 

```{r}
acce_df = 
  read_csv("./data/accel_data.csv") %>% 
  pivot_longer(
    activity.1:activity.1440,
    names_to = "minutes_of_day",
    values_to = "activities_count"
  ) %>% 
  mutate(
    minutes_of_day = sub( "activity.", "", minutes_of_day),
    minutes_of_day = as.numeric(minutes_of_day),
    weekend_or_weekday = 
      recode(day,Sunday= "weekend", Saturday = "weekend", Friday = "weekday",
             Monday = "weekday", Tuesday = "weekday", Wednesday = "weekday",
             Thursday = "weekday"),
    day = factor(day, levels= c("Monday", 
    "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday","Sunday"))) %>% 
  arrange(week, day) %>% 
  subset(select = -day_id)
  
```

The result dataset includes the week number, day of week, minutes of day, activity counts and a weekday vs weekend variables. There are total `r nrow(acce_df)` observations for recording actvity counts of every minutes in the 35 experient days.
